QALY Comparison - Living Wage Intervention

### 2023-11-09 minos/testing/QALY_comparison_energyCrises.Rmd
Updated the configs with some new packages

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
out.path <- here::here('output', 'glasgow_scaled')

base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
support.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownlift'))
noSupport.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownliftNoSupport'))

base <- read.csv(paste0(base.path, 'qalys.csv'))
support <- read.csv(paste0(support.path, 'qalys.csv'))
noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))

# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
# 
# base <- read.csv(paste0(out.path, 'qaly_baseline.csv'))
# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
# noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))

>>>>

```{r}
# # read in QALY files for baseline and interventions
# out.path <- here::here('output', 'default_config')
# #out.path <- here::here('output', 'glasgow_scaled')
# 
# base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
# support.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownlift'))
# noSupport.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownliftNoSupport'))
# 
# base <- read.csv(paste0(base.path, 'qalys.csv'))
# support <- read.csv(paste0(support.path, 'qalys.csv'))
# noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))

out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'

base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
support <- read.csv(paste0(out.path, 'qalys_support.csv'))
noSupport <- read.csv(paste0(out.path, 'qalys_nosupport.csv'))

### 2023-11-09 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Updated the configs with some new packages

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'glasgow_scaled')

base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
support.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownlift'))
noSupport.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownliftNoSupport'))

base <- read.csv(paste0(base.path, 'qalys.csv'))
support <- read.csv(paste0(support.path, 'qalys.csv'))
noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))

# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
# 
# base <- read.csv(paste0(out.path, 'qaly_baseline.csv'))
# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
# noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))

>>>>

```{r}
# # read in QALY files for baseline and interventions
# #out.path <- here::here('output', 'glasgow_scaled')
# out.path <- here::here('output', 'default_config')
# 
# base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
# support.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownlift'))
# noSupport.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownliftNoSupport'))
# 
# base <- read.csv(paste0(base.path, 'qalys.csv'))
# support <- read.csv(paste0(support.path, 'qalys.csv'))
# noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))

out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'

base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
support <- read.csv(paste0(out.path, 'qalys_support.csv'))
noSupport <- read.csv(paste0(out.path, 'qalys_nosupport.csv'))

### 2023-11-09 minos/testing/QALY_comparison_livingWage.Rmd
Fixed mistake in one of the qaly scripts
Updated the configs with some new packages

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
out.path <- here::here('output', 'glasgow_scaled')

base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
wage.path <- get_latest_runtime_subdirectory(here::here(out.path, 'livingWageIntervention'))

base <- read.csv(paste0(base.path, 'qalys.csv'))
wage <- read.csv(paste0(wage.path, 'qalys.csv'))

# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
# 
# base <- read.csv(paste0(out.path, 'qaly_baseline.csv'))
# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
# noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))
# combine the dataframes
combined <- rbind(base, wage)
```

@@

```{r}
ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'Number Individuals Receiving Intervention')

@@

ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'Ratio of living to dead in output dataframe')

@@

```{r}
sf12.plots(base = noSupport,
           base.name = 'energyDownliftNoSupport',
           int = support,
           int.name = 'energyDownlift')
```

>>>>

```{r}
# # read in QALY files for baseline and interventions
# out.path <- here::here('output', 'default_config')
# #out.path <- here::here('output', 'glasgow_scaled')
# 
# base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
# wage.path <- get_latest_runtime_subdirectory(here::here(out.path, 'livingWageIntervention'))
# 
# base <- read.csv(paste0(base.path, 'qalys.csv'))
# wage <- read.csv(paste0(wage.path, 'qalys.csv'))

out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'

base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
wage <- read.csv(paste0(out.path, 'qalys_livwage.csv'))

# combine the dataframes
combined <- rbind(base, wage)
```

@@

test <- combined %>%
  filter(intervention != 'baseline')

ggplot(test, aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'Number Individuals Receiving Intervention')

@@

# ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
#   geom_smooth() +
#   labs(title = 'Ratio of living to dead in output dataframe')

@@

```{r}
sf12.plots(base = base,
           base.name = 'baseline',
           int = wage,
           int.name = 'livingWageIntervention')
```
